---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# April 2022 General Conference of the Church of Jesus Christ of Latter-Day saints

<!-- badges: start -->
<!-- badges: end -->

Quick Analysis of The Hash tag #GeneralConference at the April 2022 General Conference of the Church of Jesus Christ of Latter-Day saints. 



```{r Libraries, warning=FALSE, include=FALSE}
library(flextable)
library(GGally)
library(ggraph)
library(igraph)
library(network)
library(quanteda)
library(sna)
library(tidygraph)
library(tidyverse)
library(tidytext)
library(tm)
library(tibble)
library(lubridate)


tweets.Conference <- read_csv("rawData/april22.csv")
```
This Histogram show the number of tweets along a time line of Conference weekend. 


```{r Histogram, echo=FALSE, warning=FALSE}
conference.Filtered <- tweets.Conference %>% 
  filter(created_at >= "2022-04-02")

ggplot(conference.Filtered, aes(x = created_at, fill = "orange")) +
  geom_histogram(position = "identity", bins = 45, show.legend = FALSE)
```

This is a sentiment analysis of the tweets that were pulled. All "bars" below the 0 line are negative. The results show the it is mostly positive.


```{r Sentiment, echo=FALSE, message=FALSE, warning=FALSE}
remove_reg <- "&amp;|&lt;|&gt;"

tidy_tweets <- conference.Filtered %>% 
  filter(!str_detect(text, "^RT")) %>%
  mutate(text = str_remove_all(text, remove_reg)) %>%
  unnest_tokens(word, text, token = "tweets") %>%
  filter(!word %in% stop_words$word,
         !word %in% str_remove_all(stop_words$word, "'"),
         str_detect(word, "[a-z]"))

tweet_sentiment <- tidy_tweets %>%
  inner_join(get_sentiments("bing")) %>%
  count(screen_name, index = ...1 %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)

ggplot(tweet_sentiment, aes(index, sentiment, fill = screen_name)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Sentiment Analysis for tweets during April 2022 Gerernal Conference",
       subtitle = "The Church of Jesus Christ of Latter-Day Saints", 
       y = "If below 0 it is a negative response", 
       x = "") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```


Updated: 03APRIL2022 at 1757 EST
